\chapter{Implementation}

\section{Overview}
The implementation of the VR Airplane Safety Training System was carried out using C\# and the StereoKit framework. The development process involved setting up the VR environment, implementing the video playback engine, and creating the interactive quiz logic.

\section{Core Components}

\subsection{Main Loop}
The application runs within a continuous loop managed by StereoKit. This loop handles input processing, state updates, and rendering for each frame.
\begin{lstlisting}[language=C#, caption=Main Application Loop]
while (SK.Step(() =>
{
    if (airplane != null) airplane.Draw(...);
    HandleMovement();
    
    switch (currentState)
    {
        case AppState.Welcome:
            ShowWelcomeScreen();
            break;
        case AppState.Video:
            UpdateVideoFrame();
            break;
        case AppState.Quiz:
            ShowQuizUI();
            break;
    }
}));
\end{lstlisting}

\subsection{Video Playback Implementation}
The video player uses OpenCvSharp to read frames from an MP4 file. These frames are then converted to a byte array and uploaded to a StereoKit texture.
\begin{lstlisting}[language=C#, caption=Video Frame Update Logic]
if (videoCapture.Read(videoFrame))
{
    // Convert BGR to RGBA
    Cv2.CvtColor(videoFrame, rgbaFrame, ColorConversionCodes.BGR2RGBA);
    
    // Update Texture
    videoTexture.SetColors(width, height, frameData);
}
\end{lstlisting}

\subsection{Quiz Logic}
The quiz system uses a list of \texttt{QuizQuestion} objects. The UI is generated dynamically based on the current question index.
\begin{lstlisting}[language=C#, caption=Quiz UI Generation]
var q = questions[quizIndex];
UI.Text(q.Text);
for (int i = 0; i < q.Options.Length; i++)
{
    if (UI.Button(q.Options[i]))
    {
        // Check answer logic
    }
}
\end{lstlisting}

\section{Challenges Faced}
\begin{itemize}
    \item \textbf{Video Synchronization:} Ensuring the audio (NAudio) and video (OpenCV) remained in sync was a challenge, solved by resetting both streams simultaneously.
    \item \textbf{VR Performance:} Initial tests showed frame drops. This was optimized by reducing the polygon count of the airplane model and using efficient texture formats.
\end{itemize}
